Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs

### 2021-02-22 NEUROC/sec7-conclusion.tex
更新Future work部分。

\section{Conclusion}
\label{sec:conclusion}

@@

>>>>

\section{Conclusion and Future Work}
\label{sec:conclusion}

@@

In this work, we analyze performance bottlenecks in a \emph{single-GPU} environment on \emph{static} graphs with the \emph{message-passing} framework.
%
Performance bottlenecks in multi-GPU/distributed GNN training/inference, dynamic graphs and other GNN frameworks are also worth studying.
%
In the future, we plan to extend our analysis of performance bottlenecks in GNN training/inference with the following directions:
%
\begin{enumerate}
    \item \emph{Multi-GPU or distributed environment.}
    %
    To handle large-scale graph datasets, multi-GPU and distributed training/inference are necessary.
    %
    These methods will inevitably introduce overheads such as inter-GPU and inter-machine communication. 
    %
    How these overheads affect performance bottlenecks is worthy to focus on.
    %
    \item \emph{Spatial-temporal graph datasets.}
    %
    Spatial-temporal graphs have dynamic topology structures.
    %
    They appear in a variety of applications like traffic speed forecasting \cite{li2018_DCRNN} and human action recognition \cite{yan2018_STGCN}.
    %
    %Learning hidden patterns from spatial-temporal graphs becomes increasingly important.
    %
    Many new GNNs are proposed to handle this kind of graphs.
    %
    How the performance bottlenecks of these GNNs are different from the classic GNNs is also worthy of in-depth study.
    %
    %Whether spatial-temporal graphs will affect performance is worthy of our attention.
    %
    \item \emph{Other GNN frameworks.}
    %
    In this work, we conducted the anlaysis with the popular message-passing framework.
    %
    Some emerging GNN learning systems also adopt different GNN frameworks like SAGA framework \cite{ma2019_neugraph} and edge-centric framework \cite{he2019_EnGN}.
    %
    Whether different frameworks lead to different performance bottlenecks is worth discussing.
\end{enumerate}
